Significant wind disturbances induced by giant dunes.

### 2021-11-19 Paper/main.tex
Re-organisation of doc

\author{First Author         \and
        Second Author \and Third Author \and \{...\}
}

\institute{F. Author \at
              first address \\
              Tel.: +123-45-678910\\
              Fax: +123-45-678910\\
              \email{fauthor@example.com}
           \and
           S. Author \at
              second address
            \and
            T. Author \at
            third address
}

>>>>

\author{Cyril Gadal \and Pauline Delorme \and Clément Narteau \and
        Giles Wiggs \and Matthew Baddock \and Joanna M. Nield \and Philippe Claudin }

\institute{C. Gadal \at
              Institut de Mécanique des Fluides de Toulouse (IMFT), Université de Toulouse, CNRS, INPT, UPS, Toulouse, France \\
              \email{cyril.gadal@imft.fr}
           \and
           S. Author \at
              second address
            \and
            T. Author \at
            third address
}
